---
name: Philip Qing An 
surname: Khor
position: Data Scientist
address: Penang, Malaysia
phone: +60 16 720 2723
www: philipscurve.com
email: pk.qa@outlook.com
github: philip-khor
linkedin: philip-khor
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Summary

Data scientist with a background in Economics and research experience in applied microeconometrics. Prior experience building proof-of-concept deep learning models, driving documentation and advocacy initiatives and developing and delivering enterprise-level data science training courses in statistics and programming.

# Work Experience and Training 

```{r}
tribble(
  ~ Company, ~ Year, ~ Position, ~ Location, 
  "Skymind AI Berhad", "October 2019 - December 2019", "Technical Writer", "George Town, Penang",
  "GRID Inc.", "May 2019 - August 2019", "Data Scientist Intern", "Minato-ku, Tokyo",
  "The Center of Applied Data Science", "July 2018 - May 2019", "Data Scientist Associate", "Bangsar South, Kuala Lumpur",
  "ASEAN Data Analytics eXchange", "Feb 2018 - June 2018", "Data Scientist Trainee", "Bangsar South, Kuala Lumpur", 
  "Penang Institute", "Aug 2016 - Jan 2017", "Research Assistant: Economics Studies", "George Town, Penang", 
  "Penang Institute", "Dec 2015 - Jan 2016", "Intern: Economics Studies", "George Town, Penang"
) %>% 
  mutate(Details = list(
    c("Prepared documentation on internally developed 
       model deployment software to support internal and external users.",
      "Provided editing assistance for development of training materials.",
      "Drove and provided support for community engagement events."),
    c("Trained real-time object detection and image segmentation
       models for use in agriculture using YOLOv2, SSD and Mask R-CNN
       deep learning architectures with internally built framework.", 
      "Delivered substantial improvement on the accuracy of number of trees 
       counted, relative to previously built internal model.", 
      "Developed metrics to evaluate model to align with client objectives.",
      "Developed pipeline consisting of Python command line interfaces to 
       facilitate preprocessing, partitioning and post-processing of image and 
       annotation data."), 
    c("Delivered over 100 hours in training sessions for Microsoft 
       Excel, R for Analytics, Tableau, Statistics and Data Storytelling.", 
      "Developed training products in the areas of statistics, 
       exploratory analysis, data visualization and machine learning 
       using spreadsheets, R, Python and Tableau delivered through 
       tools such as Jupyter Notebooks and R Markdown, focusing on 
       commercial applications of data science.",
      "Led development teams for Excel Analytics and Regression Modelling 
       and Evaluation modules.",
      "Core developer of introductory and intermediate 
       Statistics and R for Analytics modules.",
      "Worked with teams to develop and deliver training material for 
       Natural Language Processing, Neural Networks, Data Visualisation 
       with Tableau, A/B/n Testing and Time Series Analytics and Forecasting modules.", 
      "Developed internal conventions for material formatting and module code formats."), 
    c("Data science finishing school for graduates covering R and Python 
       programming modules, statistics, data preprocessing, 
       machine learning, data visualisation with 
       programming packages and interactive software, forecasting and 
       natural language processing."), 
    c("Provided research assistance for the Penang Skilled Workforce Study
       project, which identifies skills shortages and skill gaps in key
       economic sectors in Penang.",
      "Scheduled and performed interviews with Human Resource, company
       executives and other governmental and non- governmental
       stakeholders.", 
      "Liased with state and federal government agencies to obtain secondary
       data.", 
      "Emcee at the forum Budgeting Priorities in a Challenging Economic
       Environment (Nov 2016)."), 
    c("Contributed to the Penang Skilled Workforce Study, Penang Economic and Development 
       Report 2015/2016 and the Institute's evaluation of the Trans-Pacific Partnership Agreement (TPPA).", 
      "Obtained, sorted and analysed data across a wide array of sources.", 
      "Liased with government agencies to obtain data.", 
      "Prepared reports and edited report text and formatting.")
  )) %>% 
  tidyr::unnest(cols = c(Details)) %>% 
  detailed_entries(Company, Year, Position, Location, Details)
```

\newpage 
# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, 
  "Bachelor of Commerce (Honours)", "2017", "University of Wollongong", "NSW, Australia",
  "Bachelor of Commerce (Dean's Scholar)", "2014-2016", "University of Wollongong", "NSW, Australia",
  "Diploma in Business Studies", "2012-2014", "Tunku Abdul Rahman University College", "George Town, Penang"
) %>% 
  mutate(Details = list(
  c("Received the 2017 Honours Scholarship from the Faculty of Business 
     based on academic performance, research and leadership potential.", 
    "Undertook a research project as part of coursework for 
     Advanced Macroeconomic Theory (Health and wealth: economic 
     growth with endogenous health and human capital.)"), 
  c("Admitted to the Dean’s Scholar program in 
     recognition of high academic achievement.", 
    "Awarded the Business International Academic
     Merit Scholarship and the Undergraduate Excellence 
     Scholarship in recognition of prior academic achievement.", 
    "Awarded the Illawarra Regional Information Services 
     John Steinke Prize in Economics (April 2017) for achieving 
     the highest mark in 300-level Economics subjects in 2016.", 
    "Awarded the Kenneth A. Blakey Prize (March 2015) for 
     achieving the highest aggregate mark in Microeconomic Theory
     and Policy in 2014.", 
    "Consistently placed in the Dean’s Merit List (2014-2017), 
     which ranks the top 5% of students in the Faculty of Business."), 
  c("Received the Merit Scholarship amounting to 100% of the tuition fees 
     for the length of the program in recognition of prior academic performance.", 
    "Awarded Book Prize for overall academic performance."))) %>% 
  tidyr::unnest(cols = c(Details)) %>% 
  detailed_entries(Degree, Year, Institution, Where, Details)
```


# Projects 

```{r}
tribble(
  ~ project_type, ~ year, ~ project_title, ~ location, 
  "Honours thesis", "2017", "Family background and child health: the role of socioeconomic status and skills", "University of Wollongong", 
  "", "Aug 2017 - Jan 2017", "Penang skilled workforce study: labour skills for growth and change", "Penang Institute"
) %>% 
  mutate(Details = list(
    c("Econometric analysis of the relationship between parental income and
       child health status in Australia using two large Australian 
       longitudinal datasets.", 
      "Used data from the Household, Income and Labour Dynamics in Australia
       Survey (HILDA) and the Longitudinal Study of Australian Children
       (LSAC) to replicate prior longitudinal results on the effect of
       parental income on child health.", 
      "Developed a novel identification strategy to estimate the effect of
       parental resources on child health."), 
    c("Identification of skill gaps and skill shortages in major Penang
       economic sectors.", 
      "Conducted and assisted with qualitative interviews with industry
       stakeholders and human resource personnel.", 
      "Assisted in the development of questionnaires for data collection and
       development of strategies to improve response rates.", 
      "Assisted in data analysis and the preparation of visualizations for
       the report.")
  )) %>% 
  tidyr::unnest(cols = c(Details)) %>% 
  detailed_entries(project_type, year, project_title, location, Details)
```






