---
name: Philip Qing An 
surname: Khor
position: Data Scientist
address: Penang, Malaysia
phone: +60 16 720 2723
www: philipscurve.com
email: pk.qa@outlook.com
github: philip-khor
linkedin: philip-khor
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: 
  vitae::awesomecv: 
    keep_md: true
#    latex_engine: lualatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)

read_then_unnest <- function(path) {
  do.call(rbind, yaml::read_yaml(here::here(path))) |>
    as.data.frame() |>
    tidyr::unnest(cols = c(details))
} 
```

# Summary

Data scientist with a background in Economics and research experience in applied 
microeconometrics. Prior experience with regulatory modelling in the financial 
sector, building deep learning models, driving documentation and advocacy 
initiatives as well as developing and delivering enterprise data science 
training courses in statistics and programming.

# Work Experience  

```{r}
read_then_unnest("cv/src/experience.yaml") |> 
  detailed_entries(company, year, position, location, details)
```

# Publications 
```{r}
bibliography_entries("../cv/src/cvlib.bib")
```

# Projects 

```{r}
read_then_unnest("cv/src/projects.yaml") |> 
  detailed_entries(project_type, year, project_title, location, details)
```
# Education

```{r}
read_then_unnest("cv/src/education.yaml") |> 
  detailed_entries(degree, year, institution, where, details)
```
# Qualifications

```{r}
read_then_unnest("cv/src/qualifications.yaml") |> 
  detailed_entries(institution, year, qualification, where, details)
```


